Secure Composition of Robust and Optimising Compilers

### 2024-10-14 tech/acronyms.tex
tech

\newacronym{rtp}{RTP}{Robust Trace-Property Preservation}
\newacronym{tms}{TMS}{Temporal Memory Safety}
\newacronym{sms}{SMS}{Spatial Memory Safety}
\newacronym{ms}{MS}{Memory Safety}
\newacronym{specms}{SpecMS}{Speculation Memory Safety}
\newacronym{cct}{CCT}{Cryptographic Constant Time}
\newacronym{scct}{sCCT}{Strict Cryptographic Constant Time}
\newacronym{ss}{SS}{Speculative Safety}
% \newacronym{msscct}{MS+sCCT}{Memory Safety and Strict Cryptographic Constant Time}
% \newacronym{mssscct}{MS+sCCT+$\mathghost$}{Memory Safety and Strict Cryptographic Constant Time with Speculation}
\newacronym{dce}{DCE}{Dead Code Elimination}
\newacronym{cf}{CF}{Constant Folding}

\newacronym{msscct}{MCT}{Memory Safety and Strict Cryptographic Constant Time}
\newacronym{mssscct}{MCT$\mathghost$}{Memory Safety and Strict Cryptographic Constant Time with Speculation}

>>>>

\newacronym{rtp}{RTP}{Robust Trace-Property Preservation}
\newacronym{tms}{TMS}{Temporal Memory Safety}
\newacronym{sms}{SMS}{Spatial Memory Safety}
\newacronym{ms}{MS}{Memory Safety}
\newacronym{cct}{CCT}{Cryptographic Constant Time}
\newacronym{scct}{sCT}{Strict Cryptographic Constant Time}
\newacronym{msscct}{MS+sCCT}{Memory Safety and Strict Cryptographic Constant Time}
\newacronym{dce}{DCE}{Dead Code Elimination}
\newacronym{cf}{CF}{Constant Folding}
\newacronym{ss}{SS}{Speculation Safety}
\newacronym{specms}{SpecMS}{Speculation Memory Safety}

### 2024-10-14 tech/main.tex
tech

@@

\begin{definition}{\definitionlabel[\glsfirst{scct}]{def-trace-scctdef}}
  \noindent\[
  \scctsafe:=\left\{\varTrace[_{\ctsafe}] 
      \left|
        \begin{array}{l}
          \varTrace[_{\ctsafe}]=\hole{\cdot} \text{ or } \\
          \exists\varTrace[_{\ctsafe}'],\varTrace[_{\ctsafe}]=\varEvent[_{\ctsafe}];\unlock\cdot\varTrace[_{\ctsafe}'] \wedge \varTrace[_{\ctsafe}']\in\scctsafe
        \end{array}
      \right.
    \right\}
  \]
\end{definition}

\gls*{scct} may appear overly strict, since it seems that secrets must not occur on a trace (since $\varSecuritytag$ is forced to be $\unlock$). 
However, this is considered standard practice in terms of coding guidelines~\cite{ctguidelines}.
Moreover, programs that have been compiled with FaCT~\cite{cauligi2019fact} and run with a ``data independent timing mode''~\cite{arm-refman,intel-refman} enabled do not leak secrets.

@@

The combination of \gls*{ms} and \gls*{scct} is the intersection of these properties, \gls*{msscct}.
However, \gls*{ms} uses a different trace model than \gls*{scct}, so intersecting them would trivially yield the empty set. 
To remedy this issue, we introduce $\sim_{\ctsafe}: \varEvent[_{\ctsafe}] \times \varEvent[_{\mssafe}] $, a cross-language trace relation (whose key cases are presented below), that we use to intuitively unify the trace model in which the two properties are expressed:
\[
  \typerulenolabel{}{\varEvent[_{\mssafe}]\sim_{\ctsafe}\varEvent[_{\mssafe}];\unlock{}}
  \hspace{2ex}
  \typerulenolabel{}{\lightning\sim_{\ctsafe}\lightning}
  \hspace{2ex}
  \typerulenolabel{}{\emptyevent\sim_{\ctsafe}\ev{Branch\;n};\varSecuritytag{}}
  \hspace{2ex}
  \typerulenolabel{}{\emptyevent\sim_{\ctsafe}\ev{Binop\;n};\varSecuritytag{}}
\]

Essentially, $\sim_{\ctsafe}$ ignores both the new $\ev{Branch\ n}$ and $\ev{Binop\ n}$ base-events as it relates security-insensitive actions ($\unlock$) to their equivalent counterparts.
Thus, \gls*{ms} traces trivially satisfy \gls*{scct}.
% 
The above relation is extended point-wise to traces, skipping the empty event $\emptyevent$ on either side, and it is now possible to define \gls*{msscct} using the universal image:

\begin{definition}{\definitionlabel[\glsfirst{ms} and \glsfirst{scct}]{def-trace-msscctdef}}
  \[
  \msscctsafe:=\mssafe\cap\sigma_{\sim_{\ctsafe}}\left(\scctsafe\right)
  \]
\end{definition}

@@

So far, the considered trace models do not let us express speculative execution attacks such as Spectre~\cite{kocher2019spectre}. 
For this, we extend the earlier trace model so that the security tags ($\varSecuritytag{}$) carry additional information about the kind of private data leakage, i.e., the type of speculative leak.
Moreover, we add base-events signalling the beginning of a speculative execution ($\ev{Spec}$), a barrier ($\ev{Barrier}$) that signals that any speculative execution may not go past it, as well as a rollback event ($\ev{Rlb}$), which signals that execution resumes to where speculation started.

\vspace{-1em}
{
\[
  \begin{array}{rrcl}
    (\text{Base-Events}) & \varEvent[_{\mathghost}] &:=& \varEvent[_{\ctsafe}] \\
    (\text{Spectre Variants}) & vX &:=& \operatorname{NONE} \mid \operatorname{PHT} \\
    (\text{Security Tags}) & \varSecuritytag{} &:=& \lock_{vX} \mid \unlock\\ 
    (\text{Events}) & \varEvent[_{\mathghost}] &:=& \varEvent[_{\mathghost}];\varSecuritytag{} \mid \emptyevent \mid \lightning \mid \ev{Spec} \mid \ev{Rlb} \mid \ev{Barrier}\\ 
  \end{array}
\]
}

Even though the considered Spectre variants are just SPECTRE-PHT~\cite{kocher2019spectre}, NONE just describes secret data as in \gls*{scct} (see \Cref{subsec:scct:tracemodel}), the trace model is general enough to allow for potential future extension with different variants~\cite{kocher2019spectre,maisuradze2018ret2spec,horn2019zero}.
%For sake of readability, this paper just uses the notation $\lock$ in place of $\lock_{\text{PHT}}$.

\subsubsection{Speculative Safety}

@@

\begin{definition}{\definitionlabel[\glsfirst{ss}]{def-trace-ssdef}}
  \[
    \sssafe := \left\{
      \varTrace[_{\mathghost}] 
        \left|
          \begin{array}{l}
            \varTrace[_{\mathghost}]=\hole{\cdot} 
              \text{ or } 
            \exists\varTrace[_{\mathghost}'].\\
            %
            \left(\varTrace[_{\mathghost}]=\varEvent[_{\mathghost}];\unlock\cdot\varTrace[_{\mathghost}'] 
              \text{or }
            \varTrace[_{\mathghost}]=\varEvent[_{\mathghost}];\lock_{\text{NONE}}\cdot\varTrace[_{\mathghost}']\right)\\
            %
            \text{and }%
            \ \varTrace[_{\mathghost}']\in\sssafe
          \end{array}
        \right.
      \right\}
  \] 
\end{definition}
The technical setup so far leads to the above definition, where only locks annotated with $\text{SPECTRE-PHT}$ are disallowed to occur on the trace.
That way, programs attaining \gls*{ss} do not necessarily attain \gls*{scct}.

@@

As before, we need to relate the different trace models with each other, so that the memory safety property without speculation can be lifted to speculation. 
To this end, let $\sim_{\mathghost}: \varEvent[_{\mathghost}] \times \varEvent[_{\ctsafe}]$ be a cross-language trace relation whose key cases are below.
The intuition is that \gls*{ss} is trivially satisfied in \gls*{scct}, since speculation is inexpressible there, which amounts to dropping events $\ev{Spec}$, $\ev{Rlb}$, or $\ev{Barrier}$, as well as all base events tagged with $\lock_{\text{PHT}}$.

\[
  \typerulenolabel{}{\varEvent[_{\ctsafe}];\lock\sim_{\mathghost}\varEvent[_{\ctsafe}];\lock_{\text{NONE}}}
  \hspace{2ex}
  \typerulenolabel{}{\emptyevent\sim_{\mathghost}\varEvent[_{\mathghost}];\lock_{\text{PHT}}}
  \hspace{2ex}
  \typerulenolabel{}{\varEvent[_{\ctsafe}];\unlock\sim_{\mathghost}\varEvent[_{\ctsafe}];\unlock}
  \hspace{2ex}
  \typerulenolabel{}{\lightning\sim_{\mathghost}\lightning}
  \hspace{2ex}
  \typerulenolabel{}{\emptyevent\sim_{\mathghost}\ev{Spec}}
  \hspace{2ex}
  \typerulenolabel{}{\emptyevent\sim_{\mathghost}\ev{Rlb}}
  \hspace{2ex}
  \typerulenolabel{}{\emptyevent\sim_{\mathghost}\ev{Barrier}}
\]

We conclude by defining the ultimate property of interest for secure compilers: \gls*{specms}.
\begin{definition}{\definitionlabel[\glsfirst{specms}]{def-trace-specmsdef}}
  \[
  \specmssafe := \msscctsafe\cap\sigma_{\sim_{\mathghost}}\left(\sssafe\right)
  \]
\end{definition}

\subsubsection{Monitors}\label{subsubsec-cs-properties-monitors}

>>>>

\begin{definition}{\definitionlabel[\glsfirst{scct} Traces]{sccttraces}}
\[
  \begin{array}{rcll}
    \text{(Secrecy Tags)}&\varSecuritytag &:=& \unlock \mid \lock \\
    \text{(Events)}&\tmsEvent &:=& \scctAny \mid \emptyevent \mid \lightning \\ 
  \end{array}
\]
\end{definition}

@@

\begin{definition}{\definitionlabel[\glsfirst{scct}]{scctdef}}
  \noindent\[
  \scctsafe:=\left\{\scctTrace 
      \left|
        \begin{array}{l}
          \scctTrace=\hole{\cdot} \text{ or } \scctTrace=\lightning \\
          \exists\scctTrace['],\left(\scctTrace=\scctAny[\unlock]\cdot\varTrace[_{\ctsafe}'] \text{ or } \right.\\
          \hspace{2.8em}\left.\scctTrace=\emptyevent\cdot\scctTrace[']
          \wedge \varTrace[_{\ctsafe}']\in\scctsafe \right)
        \end{array}
      \right.
    \right\}
  \]
\end{definition}

\gls*{scct} may appear overly strict, since it seems that secrets must not occur on a trace (since $\varSecuritytag$ is forced to be $\unlock$). 
However, this is considered standard practice in terms of coding guidelines~\cite{ctguidelines}.
Moreover, programs that have been compiled with FaCT~\cite{cauligi2019fact} and run with a ``data independent timing mode''~\cite{arm-refman,intel-refman} enabled do not leak secrets. 
We'd like to emphasize that our goal is to motivate the core theory presented in \Cref{sec:rtpc} and not develop a new programming language.

@@

The combination of \gls*{ms} and \gls*{scct} is the intersection of these properties, \gls*{msscct}.
However, \gls*{ms} uses a different trace model than \gls*{scct}, so intersecting them would trivially yield the empty set. 
To remedy this issue, we introduce $\xlangrel{\scctsafe}{\mssafe} : \scctEvent \to \msEvent \to \mathbb{P}$, a cross-language trace relation (whose key cases are presented below), that we use to intuitively unify the trace model in which the two properties are expressed:

\begin{definition}{\definitionlabel[Mapping \glsfirst{ms} to \glsfirst{scct}]{mapping-ms-scct}}
  \newcommand{\mmap}[2]{{#1}\;{\xlangrel{\mssafe}{\scctsafe}}\;{#2}}
  \begin{center}
    \judgbox{\mmap{\msEvent}{\scctEvent}}{,,Translate \gls*{ms}-events to \gls*{scct}-events.''}

    \typerule{mapping-ms-scct-empty}{}{
      \mmap{\msev{\emptyevent}}{\scctev{\emptyevent}}
    }{mapping-ms-scct-empty}
    %
    \typerule{mapping-ms-scct-crash}{}{
      \mmap{\msev{\lightning}}{\scctev{\lightning}}
    }{mapping-ms-scct-crash}
    %
    \typerule{mapping-ms-scct-alloc}{}{
      \mmap{\msAlloc}{\scctAny[\unlock]}
    }{mapping-ms-scct-alloc}
    %
    \typerule{mapping-ms-scct-dealloc}{}{
      \mmap{\msDealloc}{\scctAny[\unlock]}
    }{mapping-ms-scct-dealloc}
    %
    \typerule{mapping-ms-scct-use}{}{
      \mmap{\msUse}{\scctAny[\unlock]}
    }{mapping-ms-scct-use}
  \end{center}
  \begin{center}
    \judgbox{\mmap{\msTrace}{\scctTrace}}{,,Translate \gls*{ms}-traces to \gls*{scct}-traces.''}

    \typerule{mapping-ms-scct-empty}{}{
      \mmap{\emptyTrace}{\emptyTrace}
    }{mapping-ms-scct-empty}
    %
    \typerule{mapping-ms-scct-cons}{}{
      \mmap{\consTrace{\msEvent}{\msTrace}}{\consTrace{\scctEvent}{\scctTrace}}
    }{mapping-ms-scct-cons}
  \end{center}
\end{definition}

%Essentially, $\sim_{\ctsafe}$ ignores both the new $\ev{Branch\ n}$ and $\ev{Binop\ n}$ base-events as it relates security-insensitive actions ($\unlock$) to their equivalent counterparts.
\gls*{ms} traces trivially satisfy \gls*{scct}, since it is assumed here that they are the result of a cryptographic constant time computation.
This may be ensured by a compiler, such as FaCT, or the semantics of the language itself.
We also don't have any other information in \gls*{scct} traces besides the secrecy tags, since the semantics of a language can simply tag relevant events with the respective vulnerability, such as a leak of secret data.
% 
It is now possible to define \gls*{msscct} using the universal image:

\begin{definition}{\definitionlabel[\glsfirst{ms} and \glsfirst{scct}]{msscctdef}}
  \[
    \msscctsafe:=\mssafe\cap\mapUniversal{\xlangrel{\mssafe}{\scctsafe}}{\scctsafe}
  \]
\end{definition}

@@

So far, the considered trace models do not let us express speculative execution attacks such as Spectre~\cite{kocher2019spectre}. 
For this, we extend the earlier trace model so that the secrecy tags ($\varSecuritytag{}$) carry additional information about the kind of private data leakage, i.e., the type of speculative leak.
This tag may be emitted by the semantics of a concrete programming language, as seen in earlier work~\cite{fabian2022automatic}. 
%Moreover, we add base-events signalling the beginning of a speculative execution ($\ev{Spec}$), a barrier ($\ev{Barrier}$) that signals that any speculative execution may not go past it, as well as a rollback event ($\ev{Rlb}$), which signals that execution resumes to where speculation started.

\begin{definition}{\definitionlabel[\glsfirst{ss} traces]{sstraces}}
{
\[
  \begin{array}{rrcl}
    (\text{Spectre Variants}) & vX &:=& \operatorname{NONE} \mid \operatorname{PHT} \mid \dots \\
    (\text{Secrecy Tags}) & \varSecuritytag{} &:=& \lock_{vX} \mid \unlock\\ 
    (\text{Events}) & \specEvent &:=& \specEvent \mid \emptyevent \mid \lightning \\ 
  \end{array}
\]
}
\end{definition}

%Even though the considered Spectre variants are just SPECTRE-PHT~\cite{kocher2019spectre}, NONE just describes secret data as in \gls*{scct} (see \Cref{subsec:scct:tracemodel}), the trace model is general enough to allow for potential future extension with different variants~\cite{kocher2019spectre,maisuradze2018ret2spec,horn2019zero}.
NONE describes secret data as in \gls*{scct} (see \Cref{subsec:scct:tracemodel}).
Any other secrecy tag, such as PHT, describes the concrete reason for the respective leak.
The trace model in \defref{sstraces} is general enough to allow for potential future extension with different variants~\cite{kocher2019spectre,maisuradze2018ret2spec,horn2019zero}.
%For sake of readability, this paper just uses the notation $\lock$ in place of $\lock_{\text{PHT}}$.

\subsubsection{Speculation Safety}

@@

\begin{definition}{\definitionlabel[\glsfirst{ss}]{ssdef}}
  \[
    \sssafe := \left\{
      \specTrace
        \left|
          \begin{array}{l}
            \specTrace=\hole{\cdot} 
              \text{ or } 
            \specTrace=\lightning
              \text{ or }
            \exists\specTrace['].\\
            %
            \left(\specTrace=\specAny[\unlock]\cdot\specTrace['] 
              \text{or }
            \varTrace[_{\mathghost}]=\specAny[\lock_{\text{NONE}}]\cdot\specTrace[']\right.\\
            \hspace{2em}\text{or }
            \left.\varTrace[_{\mathghost}]=\emptyevent\cdot\specTrace[']\right)\\
            %
            \text{and }%
            \ \varTrace[_{\mathghost}']\in\sssafe
          \end{array}
        \right.
      \right\}
  \] 
\end{definition}
The technical setup so far leads to the above definition, where only locks annotated with $\text{SPECTRE-PHT}$ are disallowed to occur on the trace.
That way, programs attaining \gls*{ss} do not necessarily attain \gls*{scct}.

@@

As before, we need to relate the different trace models with each other, so that the memory safety property without speculation can be lifted to speculation. 
To this end, let $\xlangrel{ms}{ss}: \msEvent \to \specEvent\to\mathbb{P}$ be a cross-language trace relation whose key cases are below.
The intuition is that \gls*{ss} is trivially satisfied in \gls*{ms}, since speculation is inexpressible there and a language attaining \gls*{ms} by means of semantics can enforce \gls*{ss} simply by not having a speculative dynamic semantics. 
In turn, all base events tagged with $\lock_{\text{PHT}}$ are simply dropped.

\begin{definition}{\definitionlabel[Mapping \glsfirst{ms} to \glsfirst{ss}]{mapping-ms-spec}}
  \newcommand{\mmap}[2]{{#1}\;{\xlangrel{\mssafe}{\sssafe}}\;{#2}}
  \begin{center}
    \judgbox{\mmap{\msEvent}{\specEvent}}{,,Translate \gls*{ms}-events to \gls*{ss}-events.''}

    \typerule{mapping-ms-spec-empty}{}{
      \mmap{\msev{\emptyevent}}{\specev{\emptyevent}}
    }{mapping-ms-spec-empty}
    %
    \typerule{mapping-ms-spec-crash}{}{
      \mmap{\msev{\lightning}}{\specev{\lightning}}
    }{mapping-ms-spec-crash}
    %
    \typerule{mapping-ms-spec-alloc}{}{
      \mmap{\msAlloc}{\specAny[\unlock]}
    }{mapping-ms-spec-alloc}
    %
    \typerule{mapping-ms-spec-dealloc}{}{
      \mmap{\msDealloc}{\specAny[\unlock]}
    }{mapping-ms-spec-dealloc}
    %
    \typerule{mapping-ms-spec-use}{}{
      \mmap{\msUse}{\specAny[\unlock]}
    }{mapping-ms-spec-use}
  \end{center}
  \begin{center}
    \judgbox{\mmap{\msTrace}{\specTrace}}{,,Translate \gls*{ms}-traces to \gls*{spec}-traces.''}

    \typerule{mapping-ms-spec-empty}{}{
      \mmap{\emptyTrace}{\emptyTrace}
    }{mapping-ms-spec-empty}
    %
    \typerule{mapping-ms-spec-cons}{}{
      \mmap{\consTrace{\msEvent}{\msTrace}}{\consTrace{\specEvent}{\specTrace}}
    }{mapping-ms-spec-cons}
  \end{center}
\end{definition}

We conclude with the ultimate property of interest for our secure compiler: \gls*{specms}.
\begin{definition}{\definitionlabel[\glsfirst{specms}]{specmsdef}}
  \[
    \specmssafe := \msscctsafe\cap\mapUniversal{\xlangrel{\mssafe}{\sssafe}}{\sssafe}
  \]
\end{definition}

\subsection{Monitors}\label{subsec-cs-monitors}

This part presents monitors for the properties presented in \Cref{subsec-cs-properties}.
Since all properties are safety properties, it is enough to consider trace-prefixes, i.e., finite lists of events.

\subsubsection{\gls*{tms} Monitor}\label{subsubsec-mon-tms}
In order to check \gls*{tms} on traces mechanically, we introduce a monitor that works on more abstract monitor-actions, without any other events besides those relevant to temporal memory safety.

\begin{definition}{\definitionlabel[\gls*{tms} Monitor]{monitor-tms}}
  \begin{gather*}
    \begin{aligned}
      \text{(Abstract Store)}~\tmsMonitor &\isdef\{A : \mi{Locs}, F : \mi{Locs}\} \\
      \tmsMonitor\subseteq_F \tmsMonitor['] &\text{ iff } \tmsMonitor[.F] \subseteq \tmsMonitor['.F]\\
      \varLoc\in \tmsMonitor &\text{ iff } \varLoc \in {\tmsMonitor[.A]} \wedge \varLoc \notin {\tmsMonitor[.F]}\\
      \varLoc\notin \tmsMonitor &\text{ iff } \varLoc \notin {\tmsMonitor[.A]} \wedge \varLoc \notin {\tmsMonitor[.F]}\\
      \{\varLoc\}\cup \tmsMonitor &= \{A : \{\varLoc\}\cup \tmsMonitor[.A], F : \tmsMonitor[.F]\}\\
      \tmsMonitor\setminus\{\varLoc\} &= \{A : \tmsMonitor[.A]\setminus\{\varLoc\}, F : \tmsMonitor[.F]\cup\left\{\varLoc\right\}\}\\
      \tmsMonitor\cup \tmsMonitor' &= \{A : \tmsMonitor[.A]\cup \tmsMonitor['.A], F : \tmsMonitor[.F]\cup \tmsMonitor['.F]\}\\
    \end{aligned}
  \end{gather*}
\end{definition}

The reductions are defined as follows:
\begin{definition}{\definitionlabel[\gls*{tms} Monitor Reductions]{monitor-tms-steps}}
  \begin{center}
    \judgbox{\monitorcheck[]{\tmsMonitor}{\tmsMonitor[']}{\tmsEvent}}{,,Given abstract state $\tmsMonitor$, step to abstract state $\tmsMonitor'$\\ emitting an abstract event $\tmsEvent$.''}

    \typerule{tmsmon-empty}{}{
      \monitorcheck[]{\tmsMonitor}{\tmsMonitor}{\emptyevent}
    }{tmsmon-empty}
    \typerule{tmsmon-alloc}{
      \varLoc\not\in\tmsMonitor
    }{
      \monitorcheck[]{\tmsMonitor}{\{\varLoc\}\cup\tmsMonitor}{\tmsAlloc}
    }{tmsmon-alloc}
    \typerule{tmsmon-dealloc}{
      \varLoc\in\tmsMonitor
    }{
      \monitorcheck[]{\tmsMonitor}{\tmsMonitor\setminus\{\varLoc\}}{\tmsDealloc}
    }{tmsmon-dealloc}
    \typerule{tmsmon-use}{
      \varLoc\in\tmsMonitor
    }{
      \monitorcheck[]{\tmsMonitor}{\tmsMonitor}{\tmsUse}
    }{tmsmon-use}
    \typerule{tmsmon-crash}{}{
      \monitorcheck[]{\tmsMonitor}{\tmsMonitor}{\lightning}
    }{tmsmon-crash}
  \end{center}
  \begin{center}
    \judgbox{\monitorcheck{\tmsMonitor}{\tmsMonitor[']}{\tmsEvent}}{,,Reflexive-Transitive closure of above judgement.\\$\tmsTrace$ is a list of events.''}

    \typerule{tmsmon-refl}{
      \tmsMonitor[.A]=\emptyset
    }{
      \monitorcheck{\tmsMonitor}{\tmsMonitor}{\hole{\cdot}}
    }{tmsmon-refl}
    %
    \typerule{tmsmon-trans}{
      \monitorcheck[]{\tmsMonitor}{\tmsMonitor[']}{\tmsEvent}&
      \monitorcheck{\tmsMonitor[']}{\tmsMonitor['']}{\tmsTrace}&
    }{
      \monitorcheck{\tmsMonitor}{\tmsMonitor['']}{\tmsEvent\cdot\tmsTrace}
    }{tms-trans}
  \end{center}
\end{definition}

\subsubsection{\gls*{sms} Monitor}\label{subsubsec-mon-sms}
placeholder
\subsubsection{\gls*{ms} Monitor}\label{subsubsec-mon-ms}
placeholder
\subsubsection{\gls*{scct} Monitor}\label{subsubsec-mon-scct}
placeholder
\subsubsection{\gls*{msscct} Monitor}\label{subsubsec-mon-msscct}
placeholder
\subsubsection{\gls*{ss} Monitor}\label{subsubsec-mon-spec}
placeholder
\subsubsection{\gls*{specms} Monitor}\label{subsubsec-mon-specms}
placeholder

%%%%%%%%%%%%%

\subsection{$\src{RusT}$- A Temporal Memory Safe Language}\label{subsec-rust}
placeholder
\subsubsection{Syntax}\label{subsec-rust-syntax}
placeholder
\subsubsection{Static Semantics}\label{subsec-rust-static}
placeholder
\subsubsection{Dynamic Semantics}\label{subsec-rust-dynamic}
placeholder
\subsubsection{Properties}\label{subsec-rust-properties}
placeholder

%%%%%%%%%%%%%

\subsection{$\irl{CePeEs}$- An Intermediate Representation}\label{subsec-cepees}
placeholder
\subsubsection{Syntax}\label{subsec-cepees-syntax}
placeholder
\subsubsection{Static Semantics}\label{subsec-cepees-static}
placeholder
\subsubsection{Dynamic Semantics}\label{subsec-cepees-dynamic}
placeholder
\subsubsection{Properties}\label{subsec-cepees-properties}
placeholder

%%%%%%%%%%%%%

\subsection{Compiler from $\src{RusT}$ to $\irl{CePeEs}$}\label{subsec-rust-to-cepees}
placeholder
\subsubsection{Secure Compiler}\label{subsec-rust-to-cepees-seccomp}
placeholder

\subsection{Bounds-Check Instrumentation in $\irl{CePeEs}$}\label{subsec-softbounds-in-cepees}
placeholder
\subsubsection{Secure Compiler}\label{subsec-softbounds-cepees-seccomp}
placeholder

\subsection{Improved Compiler from $\src{RusT}$ to $\irl{CePeEs}$}\label{subsec-improved-rust-to-cepees}
placeholder
\subsubsection{Secure Compiler}\label{subsec-improved-rust-to-cepees-seccomp}
placeholder

\subsection{Dead Code Elimination in $\irl{CePeEs}$}\label{subsec-dce-in-cepees}
placeholder
\subsubsection{Secure Compiler}\label{subsec-dce-cepees-seccomp}
placeholder

\subsection{Constant Folding in $\irl{CePeEs}$}\label{subsec-cf-in-cepees}
placeholder
\subsubsection{Secure Compiler}\label{subsec-cf-cepees-seccomp}
placeholder

\subsection{Optimising Compiler from $\src{RusT}$ to $\irl{CePeEs}$}\label{subsec-optimising-rust-to-cepees}
placeholder
\subsubsection{Secure Compiler}\label{subsec-optimising-rust-to-cepees-seccomp}
placeholder

%%%%%%%%%%%%%

\subsection{$\obj{A}$ - An Assembly-Like Target}\label{subsec-a}
placeholder
\subsubsection{Syntax}\label{subsec-a-syntax}
placeholder
\subsubsection{Static Semantics}\label{subsec-a-static}
placeholder
\subsubsection{Dynamic Semantics}\label{subsec-a-dynamic}
placeholder
\subsubsection{Properties}\label{subsec-a-properties}
placeholder

%%%%%%%%%%%%

\subsection{Compiler from $\irl{CePeEs}$ to $\obj{A}$}\label{subsec-cepees-to-a}
placeholder
\subsubsection{Secure Compiler}\label{subsec-cepees-to-a-seccomp}
placeholder

\subsection{Compiler from $\src{RusT}$ to $\obj{A}$}\label{subsec-rust-to-a}
placeholder
\subsubsection{Secure Compiler}\label{subsec-rust-to-a-seccomp}
placeholder

%%%%%%%%%%%%

\subsection{$\ird{SpA}$ - An Assembly-Like Target with Speculation}\label{subsec-spa}
placeholder
\subsubsection{Syntax}\label{subsec-spa-syntax}
placeholder
\subsubsection{Static Semantics}\label{subsec-spa-static}
placeholder
\subsubsection{Dynamic Semantics}\label{subsec-spa-dynamic}
placeholder
\subsubsection{Properties}\label{subsec-spa-properties}
placeholder

%%%%%%%%%%%%

\subsection{Compiler from $\obj{A}$ to $\ird{SpA}$}\label{subsec-a-to-spa}
placeholder
\subsubsection{Secure Compiler}\label{subsec-a-to-spa-seccomp}
placeholder

\subsection{Compiler from $\src{RusT}$ to $\ird{SpA}$}\label{subsec-rust-to-spa}
placeholder
\subsubsection{Secure Compiler}\label{subsec-rust-to-spa-seccomp}
placeholder
